\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}

### 2021-03-17 papers/intro_paper/results_synthetic.tex
changes in Sec. IIIB

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
        \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
        \caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$). Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
        \label{fig:nongr_waveform}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, we investigate the impact on the estimation of \ab{the} GR parameters
\sout{discussed in Sec.~\ref{sec:method},} $\bxigr$ as we change the
magnitude of deviation in the non-GR parameters. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. We summarise the results in
Fig.~\ref{fig:gr_ngr_comparison}. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. Since the
measurement of the frequency and damping time in the $\pSEOB$ model
incorporate information from the masses and spins through the NR
fitting formulae (as shown in
Eqs.~(\ref{eq:nongr_freqs_a})---(\ref{eq:nongr_freqs_b})), one might have
expected correlations between the mass, spins and the QNM frequencies,
leading to biased estimates in the masses and spins. We confirm here
that is not the case.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
        \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
        \caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$). Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) \comment{AB: what is the amplitude $h$? How is it obtained from the polarizations?} and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
        \label{fig:nongr_waveform}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, we investigate the impact on the estimation of \ab{the} GR parameters
\sout{discussed in Sec.~\ref{sec:method},} $\bxigr$ as we change the
magnitude of deviation in the non-GR parameters. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. We summarise the results in
Fig.~\ref{fig:gr_ngr_comparison}. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. Since the
measurement of the frequency and damping time in the $\pSEOB$ model
incorporate information from the masses and spins through the NR
fitting formulae (as shown in
Eqs.~(\ref{eq:nongr_freqs_a})---(\ref{eq:nongr_freqs_b})), one might have
expected correlations between the mass, spins and the QNM frequencies,
leading to biased estimates in the masses and spins. We confirm here
that is not the case. \comment{AB: I don't see how from the figure O 
conclude that there are no correlations between masses/spins and QNMs.}
